\documentclass[10pt,a4paper]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[scale=0.85]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=2pt}

% Personal Info
\name{Siam Hossain}{Nayon}
\address{Dhaka 1230, Bangladesh}{}{}
\phone{+8801873086894}
\email{siamhossain1130@gmail.com}
\social[github]{siam-hossain9}

\begin{document}
\makecvtitle

%--------------------
% Summary
%--------------------
\section{Summary}
\cvitem{}{
Graduate Computer Science \& Engineering student interested in backend, frontend, and full-stack development.
Comfortable building end-to-end projects, working with Git, and learning production practices (testing, CI/CD, code review).
Strong fundamentals in programming and problem solving; also experienced with applied ML projects.
}

%--------------------
% Education
%--------------------
\section{Education}
\cventry{}{BSc in Computer Science and Engineering}{American International University}{Dhaka, Bangladesh}{Final Year}{}
\cventry{}{HSC (Science)}{Dhaka Commerce College}{Dhaka, Bangladesh}{}{}

%--------------------
% Skills
%--------------------
\section{Technical Skills}
\cvitem{Languages}{Python, JavaScript, C++, Java, C\#}
\cvitem{Web}{HTML, CSS, JavaScript, REST APIs}
\cvitem{Tools}{Git/GitHub, VS Code, Terminal}
\cvitem{ML}{PyTorch, CNN, CLIP, DINOv2}
\cvitem{Hardware}{Arduino, sensors, servo motors, OLED displays}

%--------------------
% Projects
%--------------------
\section{Selected Projects}

\cvitem{Dororo -- Web App}{
Full-stack content discovery platform for movies, TV shows, and anime. Integrates four public APIs (TMDB, OMDB, TVMaze, AniList), features client-side search with suggestions, a localStorage watchlist, and is deployed via Vercel. Built with vanilla HTML, CSS, and JavaScript.
\newline\small\textit{GitHub:} \href{https://github.com/siam-hossain9/dororo}{\nolinkurl{github.com/siam-hossain9/dororo}}
}

\cvitem{Few-Shot Classification}{
Implemented few-shot learning using pretrained models (DINOv2, CLIP, ViT, ResNet). Achieved 98.85\% accuracy on CUB-200 and 99.97\% on Oxford Flowers datasets.
\newline\small\textit{GitHub:} \href{https://github.com/siam-hossain9}{\nolinkurl{github.com/siam-hossain9}}
}

\cvitem{CNN Image Classifier}{
Built a multi-class CNN using PyTorch with batch normalization, dropout, and data augmentation.
\newline\small\textit{GitHub:} \href{https://github.com/siam-hossain9}{\nolinkurl{github.com/siam-hossain9}}
}

\cvitem{Weather Prediction}{
Developed machine learning models for predictive analysis using real-world weather datasets.
\newline\small\textit{GitHub:} \href{https://github.com/siam-hossain9}{\nolinkurl{github.com/siam-hossain9}}
}

\cvitem{Smart Home System}{
Designed Arduino-based automation system with sensors and servo-controlled responses.
\newline\small\textit{GitHub:} \href{https://github.com/siam-hossain9}{\nolinkurl{github.com/siam-hossain9}}
}

\cvitem{Reaction Time Game}{
Created a 3-player Arduino game with OLED display and real-time interaction logic.
\newline\small\textit{GitHub:} \href{https://github.com/siam-hossain9}{\nolinkurl{github.com/siam-hossain9}}
}

\cvitem{OpenGL Village}{
Built a 3D graphical scene using OpenGL and GLUT.
\newline\small\textit{GitHub:} \href{https://github.com/siam-hossain9}{\nolinkurl{github.com/siam-hossain9}}
}

\cvitem{Bank System}{
Developed C++ banking application with file handling and OOP design.
\newline\small\textit{GitHub:} \href{https://github.com/siam-hossain9}{\nolinkurl{github.com/siam-hossain9}}
}

\cvitem{Snake Game}{
Implemented classic game with multiplayer mode and score tracking.
\newline\small\textit{GitHub:} \href{https://github.com/siam-hossain9}{\nolinkurl{github.com/siam-hossain9}}
}

%--------------------
% Experience
%--------------------
\section{Experience}
\cventry{}{Freelance SEO Specialist}{Remote}{}{}{
Worked on keyword research, content optimization, and improving website rankings.
}

%--------------------
% Publication
%--------------------
\section{Publication}
\cvitem{}{
Research paper on Few-Shot Fine-Grained Image Classification demonstrating high-accuracy results using pretrained models.
}

%--------------------
% Interests
%--------------------
\section{Interests}
\cvitem{}{Robotics, Research}

\end{document}
